Sparse Function-space Representation \\ of Neural Networks

### 2023-05-13 paper/main.tex
updating rl stuff

\textbf{Model-based reinforcement learning}
We now detail how our method can be used in model-based RL.
Folling the Markov decision process formulation \cite{bellmanDynamic1956}, we
denote states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \), actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\) and
transition dynamics \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \) subject to  i.i.d. transition noise \(\noise_{t}\).
The goal of RL is to find the policy \(\pi \in \Pi \) that maximises the sum of rewards
in expecation over the transition noise,
\begin{align} \label{eq-model-free-objective}
\policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \left[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \right]
\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}.
\end{align}
where $\gamma \in [0, 1]$ is a discount factor to account for the infinte sum.

>>>>

\textbf{Model-based reinforcement learning}
We now detail how our method can be used in model-based RL.
Folling the Markov decision process formulation \cite{bellmanDynamic1956}, we
denote states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \), actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\) and
transition dynamics \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \).
The goal of RL is to find the policy \(\pi : \stateDomain \rightarrow \actionDomain \), that maximises the sum of rewards
\begin{align} \label{eq-model-free-objective}
\policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \left[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \right]
\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}.
\end{align}
in expecation over the transition noise,
 subject to  i.i.d. transition noise \(\noise_{t}\).
where $\gamma \in [0, 1]$ is a discount factor to account for the infinte sum.
